\documentclass{article}

\setlength{\parskip}{1in}
\centering
\pagenumbering{gobble}

\begin{document}
	i need you to read this.

	i need you to read this carefully and slowly.

	\newpage
	i need you to linger on each page.

	don't look away.

	join the clean white void.

	\newpage

	this is about listening.

	i need you to listen.
	\newpage

	listen with your body.

	listen to your limbs.

	listen to the edges of your self.

	be conscious of the air around us. 

	this is our space.

	\newpage

	listen to these words.

	your mind will make a melody.\newpage

	inner words take forms-

	rhythms-

	texture.\newpage

	this is your voice, do you recognise it?

	\newpage

	listen outside your self.

	the air around you is full of small sounds.

	the building breathes - fresh and stale air.

	it is a cycle.\newpage

	breathing in and out is a way of making a circle.

	the pure sound is a perfect circle.

	\newpage

	listen further outwards. 
	
	avoid objects.\newpage

	a sound is its own object.

	listen to the sound without cause.

	listen to the nameless fwoosh. the unknown thwunk.

	don't pretend you've heard these sounds before.

	that was then. this is now.

	\newpage

	listen to the page you just turned.

	thin.

	crisp.\newpage

	tear the page.

	slowly.

	quickly.

	\emph{louder}.

	\newpage

	take out a page.

	hold it right against your ear and scrunch it into a ball.

	i don't care if it hurts.

	i need you to listen.

	\newpage

	can we talk?

	\newpage

	small things really bother me, they keep me awake.

	people moving, thinking, living.

	\newpage

	there's this heaviness in my chest.

	do you ever get that?

	its like my brain is all flailing wires, nothing ever comes together.

	outside it's really still and cool.\newpage

	i wish you could be like that.\newpage

	far off - clicks of doors closing, hum of neon.

	insistant pumps overhead mean time is passing.

	lungs barely move.

	so close to stasis.

	close.\newpage

	why can't i feel this quiet?\newpage

	tiny songs next door, underbreath and muttered.

	low resonance of distant word,

	carries person and breath.\newpage

	i need you to listen inside your mouth,

	feel your tense jaw, 

	strains of tight red electricity,

	piercing downwards,

	inwards,

	screaming.\newpage

	i can barely hear you,

	you're right here,

	but nothing is making it through.\newpage

	everything is twisted,

	contortions.

	when things happen they are harsh,

	scraping,

	screaming,

	booming.\newpage

	when you think about your body,

	does it feel weak?

	mush and meat,

	liquid resistance,

	persistant puddle.\newpage

	it takes a lot of effort to break things down,

	immense weights,

	combined,

	conflicting,

	crashing.\newpage

	once someone beat me down,

	repeated blows,

	mush and meat.

	you can't beat someone up,

	only down.\newpage


	it takes a lot of effort to break things down.

	it can happen in an instant.

	it can happen to you.\newpage

	i can barely hear you,

	nothing makes it through,

	i can't listen through chaos/

	\newpage

	if you break down these words,

	they can become harsh noise.\newpage

	the tongue, 

	the lips,

	the throat-

	they perform,

	they contort.\newpage

	``KSHGH"

	``KREAWGN"

	``SHFHHHDJGHhh"

	``BOUDGJYAHhhhhhhhhmmnnnrrghhr"\newpage

	when something sounds crazy,

	dangerous,

	out of control-

	it's only a matter of complexity.

	too many voices.\newpage

	around here things gently crash.

	dissolving, dead.

	a raindrop, individuated, 

	for now.\newpage

	white noise constant.

	smiling, 

	cosy,

	cold.\newpage

	if i were a raindrop i would hurl myself at the ground,

	in sacrifice,

	trying to soften up the concrete world.\newpage

	tearing, slight banging,

	splats,

	squeaks,

	rubber, water and concrete.\newpage

	if we were here,

	togther and wet,

	smiling,

	cosy,

	cold.\newpage

	you'd hear me hurl myself at the ground,

	in sacrifice,

	faint squeak -

	heavy, wet thwack,

	rubber, water, concrete,

	outward gasp,

	inward groan,\newpage

	white noise constant -

	a body in prayer
	\newpage

	listening inside my mouth,

	jaw clenched, tight red electric,

	greeting it i find release.\newpage

	sometimes seeing you i can let go.\newpage

	outside, just over there, jarring cycles.

	your body has four corners,

	each of them set like a spring -

	\newpage

	can you hear the roaring world?

	it's just over there.

	jarring cycles.

	try again closely/ 

	stop. start.\newpage

	the roaring world has its home too,

	everyone at once trying to get there.

	squeals, cries, shouts,

	shouting towards someone's idea of home.\newpage

	when wheel touches earth it makes almost no sound.

	twenty thousand revolutions per minute.

	just over there.

	jarring cycles.\newpage

	low earth, heavy rubber, everyone all at once,

	screeching black,

	someone's idea of home.\newpage

	if we are still right now,

	if we can breathe.

	sharp fumes, heavy, burnt.

	if we can be still we can hear the roaring world,

	everyone at once.

	\newpage
	
	in trees,

	there are tiny hearts,

	pounding.\newpage

	birdbrain forcing out song,

	screams.\newpage

	nothing is still.

	cool breeze, sharp sun.

	``garden."

	can you just be still?

	fuck.\newpage

	everywhere, someone else, making some small sound

	even trees move.

	look, can you do me a favour?

	yep?

	then stop fucking moving.\newpage

	i'm not even kidding.

	this sucks.\newpage

	we can't keep on like this.

	inside of you, you are wild.

	it's too much, i need you to stop.\newpage

	outside, in the distance,

	thundering machines.

	they won't stop.\newpage

	go up to them.

	touch them.

	put your hand inside until you feel blood.\newpage

	outside, so much screaming.

	don't join in.

	be apart, 

	alone.\newpage

	outside in the cool air,

	bare skin,

	bumpy flesh,

	stinging.\newpage

	you are rare,

	i need you to stay separate,

	alone.

	still.\newpage

	i know inside you are wild,

	you are rare,

	but please just be fucking still.\newpage

	i know you are a special kind of child.

	you think aloud in billowing dreams.

	you think.

	i am not your mother.\newpage

	just listen to yourself.

	you are not as large as you think.

	go stand outside, in thundering machines,

	think about what is inside you.\newpage

	stand with bare skin, 

	stinging.

	put your hand inside yourself until you feel blood.

	do it again.\newpage

	this face is puffy and full of ghosts,

	cold air, ripped flesh - \newpage

	that stupid mouth, for gorging, belching,

	ranting.

	inside it's swollen and pierced,

	put your hand inside until you feel blood.\newpage

	inside your chest is a slow, thudding, 

	reluctant beat.

	it can't be still.

	i heard it's shrinking.

	\newpage
	monstrous howling,

	breaks at the edges,

	strained,

	stripping the throat.\newpage

	you scream,

	i see your tears,

	baby,

	and i don't care.\newpage

	the sky is peaceful,

	somewhere else there is laughter,

	friendship/

	\newpage

	i can't breathe in your presence, 

	there's no room.

	you flail frantic,

	i don't care.\newpage

	small explosions,

	careful,

	push people around, through the world.

	you explode sometimes.\newpage

	your face is wet and salty and red,

	i'm a long way away.

	i hear your nose, dripping.\newpage

	in my chest is a reluctant little pump,

	if it could stop it would,

	it's tired.

	on. and on. and on.

	always.\newpage
	empty.\newpage
	some kind of cave.

	bright flickering lights.

	everything we say reverberates for weeks.\newpage

	do you believe in ghosts?

	sometimes it feels like someone is taking my words,

	spitting them out in other place.

	other body.\newpage

	have you ever thought that your voice is not yours?

	you say a word,

	it leaves your body.

	other.

	filth.\newpage

	when we speak our voices touch the other person's body,

	it can be tiny,

	and close,

	but you touch me,

	from afar.\newpage

	things keep swooshing by my head,

	crazy, flapping, mad.

	their sounds are stolen,

	other places,

	other bodies.\newpage

	rubber clacking floor,

	hard walls,

	glass bodies,

	winds of voice.\newpage

	it's hard to get away from yourself,

	everything we say reverberates for weeks,

	other place,

	other body.

	\newpage
	this body is three walls,

	and a mouth.

	we yawn and spew and squeal.

	our bowels rumble.\newpage

	you enter me.

	i contain you, 

	briefly.

	we fall and you leave,

	confused.\newpage

	when we are together we can rattle,

	yawn, spew and squeal.

	bowels rumble but it's never quick enough.\newpage

	this body,

	three walls and a mouth.

	empty,

	quiet,

	falling.\newpage

	it's a deal,

	us together.

	you said you'd do it-\newpage

	c'mon,

	make the commands,

	i'll be here,

	i'll fall.\newpage

	skin on cool hard metal,

	mouth open

	/shut.

	\newpage
	i'll be still while we hum,

	insects in the ceiling electric,

	a halo.\newpage

	you make us rise-

	say the word,

	make the command,

	i'll fall.
	\newpage

	there's a faint hiss,

	in your ears or world.\newpage

	outside lunatics roar and race,

	full moon.

	small creatures stir,

	tiny hearts sleep in trees and rooftops.\newpage

	this house hums,

	innate resonance,

	cyclical,

	rectangular,

	electric.\newpage

	heavy eyes,

	startled in cold light,

	slow,

	empty,

	still.\newpage

	chest rising

	/falling\newpage

	it is a cycle,

	a kind of circle,

	rectangular, electric,

	cold.\newpage

	outside in predawn solitude,

	shadowstreets,

	otherself,

	memories of drunken and hurt,

	tamar friends,

	idiotic gulls screaming.\newpage

	machines bellow,

	smoke sings twisted,

	floating sheets.

	under sodium,

	shadows of containers,

	carriages.\newpage

	the steam on your breath,

	the bumps on your flesh,

	skin stinging,

	a body in prayer,

	you pierce me,

	i hurl myself to the ground,

	put my hand inside bellowing machine,

	roaring idiot,

	screeching black,

	tiny hearts pounding,

	someone's idea of home,

	billowing dreams,

	not yr mother,

	not yr mum,

	``i love you/i'm worthless",

	a stolen prayer,

	face puffy full of ghosts,

	i did it again, i put my hand inside myself until i felt blood,

	angels on my body, ghosts all inside me,\newpage

	``garden",

	possum falls out of bed: 7am new years day 2012,

	crow falls dead: midlands highway 1999,

	she hurls herself to the ground, body in prayer: wherever you are // 
	predawn // under sodium // under shadow // steam on your breath 2016
\end{document}
